Foregrounds in Wide--Field Redshifted 21~cm Power Spectra

### 2015-02-23 ms.tex
Change "alternate" interpretations of pitchfork to two related effects
from fa05a33:
============

In ms.tex,

(*) Change "alternate" interpretations of pitchfork effect to two
related effects contributing to it based on Judd's suggestion

We interpret this as due to equal--sized delay bins subtending larger solid angles near the horizon thereby containing larger integrated emission. An alternate, but related, interpretation is that baseline vectors (including those with largest lengths) are foreshortened towards the horizon along their orientation. Thus, they become sensitive to larger angular scales that match the inverse of their foreshortened lengths along these directions.

@@

We find that all wide--field instruments, typical of modern EoR observatories, imprint a characteristic {\it two--pronged fork} signature in delay spectra. There are two related interpretations: delay bins near the horizon subtend larger solid angles and therefore contain larger integrated emission; and, foreshortening of baselines towards the horizon makes them sensitive to emission on large angular scales which match the inverse of their foreshortened lengths. These effects combined with higher sensitivity of antennas in the primary field of view results in a characteristic {\it pitchfork} signature. The amplitude of these generic signatures can be controlled by careful design of antenna aperture. In contrast to a dipole and a phased array such as an MWA tile, a dish such as the one proposed for HERA is found to yield the least foreground contamination and thus preferable for EoR studies.

>>>>

We interpret this as due to equal--sized delay bins subtending larger solid angles near the horizon thereby containing larger integrated emission. Further, baseline vectors (including those with largest lengths) are foreshortened towards the horizon along their orientation. Thus, they become sensitive to larger angular scales that match the inverse of their foreshortened lengths along these directions.

@@

We find that all wide--field instruments, typical of modern EoR observatories, imprint a characteristic {\it two--pronged fork} signature in delay spectra. This arises from two related effects: delay bins near the horizon subtend larger solid angles and therefore contain larger integrated emission; and, foreshortening of baselines towards the horizon makes them sensitive to emission on large angular scales which match the inverse of their foreshortened lengths. These effects combined with higher sensitivity of antennas in the primary field of view results in a characteristic {\it pitchfork} signature. The amplitude of these generic signatures can be controlled by careful design of antenna aperture. In contrast to a dipole and a phased array such as an MWA tile, a dish such as the one proposed for HERA is found to yield the least foreground contamination and thus preferable for EoR studies.
